\chapter{Method}
\label{chap:method}
This chapter will go over the methods I will be using when performing my study, and will cover how I identify, construct, and conduct my study population and sampling, the data collection, and the data analysis. First of all, I give my reasoning for the methods that I chose, and how they are appropriate for my research questions and the procurement of the desired results. 

\section{Choice of methods}
The paper by Rahim et al. \cite{rahim_et_al} reviews approaches to assessing cybersecurity awareness. The authors captured 23 studies from 2005 to 2014, and categorised them by assessment method, target audiences, coverage of assessment and assessment goals, among other things. It found that very few studies focused on youngsters and on the issue of protecting personal information, while most studies are focused on organisations. The value in this paper for me is a taxonomy of methods which I can use as inspiration. One of the target audiences are home users, which is what my thesis will focus on. Most of these studies used a survey-based questionnaire, which could indicate that this is a good option. However, it can also mean that there should be some diversity in the methodology targeting these groups. Other papers, which had similar goals to mine, for the most part used questionnaires. 

In the sections below I will argue for the use of this method to answer my research questions. 

\subsection*{RQ1: What is the current security awareness level of smart home users in Norway?}
A quantitative method is appropriate for investigating the security awareness level due to the fact that you are able to quantify the specific levels with numbers. This can lead to a more accurate representation of their security awareness, rather than if I had to infer it by qualitative analysis. 

\subsection*{RQ2: What are some of the most common pitfalls of smart home users in Norway which impose risk amplification?}
When using a questionnaire, you can ask questions that seek to uncover different usage patterns and user behaviours. Risk experts mostly know what types of behaviour that can impose risk amplification. Therefore, using predefined answers will be able to uncover the common pitfalls of smart home users. 

\subsection*{RQ3: What do smart home users in Norway perceive being the highest security risks when using smart home devices?}
By identifying related work on risk perceptions, I have uncovered a sizeable amount of potential risk scenarios which I can use to verify what risks are perceived as the highest by the respondents. This can be presented to the respondents as a series of risk scenarios where they will rank the them on a likert scale to determine their perceived risk. 

\subsection*{Final thoughts}
In addition to the thoughts above, I may also need to include a question where the respondent can voice their thoughts freely on the questionnaire in order to fully cover these research questions, and possibly other things I may have missed. This will slightly reduce the negative aspects of a survey based data collection in comparison to a semi-structured interview for example. 

\section{Study population and sampling}
The data gathering methodology will include a questionnaire given to a sample of the Norwegian population. I will utilise non-probability sampling since the target group comprise people who own and/or uses smart home devices in their daily lives. Furthermore, the sample will be constructed as a convenience sample, due to the difficulty of reaching out to other sample types. When creating the sample it is important to note that the response rate is about 10-15 per cent, therefore the sample size must be ten times the expected response. 

\section{Data collection}
To collect the data for my thesis, I will be using a questionnaire as my primary quantitative research method. 
In order to answer my research questions, I will create a number of hypotheses' to aid in measuring the security awareness level, as well as the most common pitfalls and highest perceived risks. Since this is a quantitative approach, I have to use close-ended questions, which means that responses are predefined. The distribution vector will be through a Facebook group for smart home enthusiasts in Norway, which contain between eight and nine thousand people. The tool for creating the questionnaire will be Nettskjema, which is an NTNU affiliated resource. In addition to the main data collection, I will also collect data from a control group to compare results. The distribution vector for this sample will be my own network on Facebook, so it may contain bias. The questions for this sample will be reformatted to be receptive for respondents who does not own any smart devices, although they will still try to measure the same aspect. Some of the questions that cannot easily be changed to fit both groups will only be answered by people who owns smart home devices. 

When creating the questions I have relied on a couple of sources to guide me. In order to assess the security awareness, I have relied on a document from ENISA called ``Security and Resilience of Smart Home Environments: Good practices and recommendations'' \cite{ENISA2015SmartHome}. In Annex D of this document, they go over topics for user awareness and best practises for the consumer. This annex explains how to choose, operate, and use online services for smart home devices securely. I have based my questions on these practises to collect the necessary data about the users security awareness level. I have also used other sources \cite{Awad2018} \cite{Caviglione2015} \cite{Schaik2017} to create questions from. Especially when it comes to finding risk scenarios, which I will ask the respondents to rate according to their perception of the risk. Additionally, I have also brainstormed topics for questions myself. 

The final questionnaires that were used for the main sample and the control group are included in Annex \ref{app:questionnaire_form} and Annex \ref{app:controlgroup_questionnaire_form}. 

\section{Data analysis}
When analysing the data it is important to understand that biases may exist and that an either-this-or-that dichotomy is not necessarily the best way to think about it. According to a book by Leedy and Ormrod \cite{pracres}, quantitative researchers may use a constructivist framework when approaching a research question, while qualitative researchers usually think in a postpositivist manner. However, many also acknowledge that both absolute truths may exist, and that self-constructed beliefs and biases are legitimate objects of study in itself. This way of thinking is usually labelled as pragmatism and realism and is the general mindset I will focus on while analysing the data. 
The number of respondents (N) of each sample was 222 for the main sample, and 43 for the control group. 

\subsection{Analysis procedure}
For analysis, I used the statistical program IBM SPSS, as well as Excel spreadsheets and other minor tools. In the following sections I will give a summary of the statistical methods that I used in the analysis. 

I started analysis of every question with a descriptive analysis, seeking to identify the distribution in percentage and count. Further, I have performed univariate analysis of individual questions and visualised the results mostly in regular vertical bar charts, however I also used tables and stacked horizontal bar charts where appropriate. 

After these questions were analysed, I performed bivariate analysis of multiple questions to search for differences and similarities between for example categorical groups and continuous variables. I did this to test the hypothesis that there were differences between the groups. The null hypothesis I used was that there are no significant difference between the groups. When doing the analysis, the yes and no answers were given the values of yes = 1 and no = 2. In questions were knowledge were analysed, I gave the knowledge levels the values of 1 to 4. I have used ANOVA (analysis of variance) to check for statistical significance, in which I used the standard P = 0.05. P stands for probability and indicate how probable it is that the results are due to chance alone. When P is less than 0.05 it means that the probability of this result being due to chance is less than 5\%, and provides a good argument for discarding the null hypothesis. I started by performing ANOVA with demographics data as my independent variable, which I cross-checked with all the relevant questions. Then I moved on to other variables I found could be interesting to look at during the univariate analysis. 

I analysed the control group in the end, and performed an univariate analysis of the questions which I compared to the results in the main sample. I first looked at the demographics and background of the sample to get an overview how how it looked like. Then I went through every question and compared the distribution to the main sample and noted the questions that had the largest divergent answers and reported on those. 

\textcolor{red}{WIP: Maybe in discussion?} 
Many have criticised the use of ANOVA of ordinal data like likert-scales, small sample sizes, unequal variances, and non-normal distributions, and says that parametric statistics cannot be used because of this. However, a Paper by Norman \cite{Norman2010} breaks down these arguments and show that parametric statistics are in fact robust, and can be used without concern for getting wrong answers. This is also consistent with empirical literature dating back nearly 80 years \cite{Norman2010}. 

\section{Ethical and legal considerations}
\textcolor{red}{WIP}
This thesis will collect data about respondents which need to be anonymous. I also need to consider the privacy aspect of the information I collect. For legal considerations, I need to avoid collecting data which can turn out to be identifiable if put together since the data should be anonymous. I have reported my project to the Norwegian Center for Research Data (NSD), and have gotten my project approved. Initially I wanted to let the people leave their email addresses if they wished to receive the report when finished since I assumed a lot of people in my sample would think it would be interesting to read. However, I later removed this option in order to make the questionnaire completely anonymous. 



\begin{comment}
The structure of the thesis, i.e., which chapters and other document elements that should be included, depends on several factors such as the study level (bachelor, master, PhD), the type of project it describes (development, research, investigation, consulting), and the diversity (narrow, broad). Thus, there are no exact rules for how to do it, so whatever follows should be taken as guidelines only.

A thesis, like any book or report, can typically be divided into three parts: front matter, body matter, and back matter. Of these, the body matter is by far the most important one, and also the one that varies the most between thesis types.

\section{Front Matter}
\label{sec:frontmatter}

The front matter is everything that comes before the main part of the thesis. It is common to use roman page numbers for this part to indicate this. The minimum required front matter consists of a title page, abstract(s), and a table of contents. A more complete front matter, in a typical order, is as follows.

\begin{description}
    \item[Title page:] The title page should, at minimum, include the thesis title, authors and a date. A more complete title page would also include the name of the study programme, and possibly the thesis supervisor(s). See \cref{sec:setup}.
    \item[Abstracts:] The abstract should be an extremely condensed version of the thesis. Think one sentence with the main message from each of the chapters of the body matter as a starting point. \textcite{landes1951scrutiny} have given some very nice instructions on how to write a good abstract. A thesis from a Norwegian Univeristy should contain abstracts in both Norwegian and English irrespectively of the thesis language (typically with the thesis language coming first).
    \item[Dedication:] If you wish to dedicate the thesis to someone (increasingly common with increasing study level), you may add a separate page with a dedication here. Since a dedication is a personal statement, no template is given. Design it according to your preference.
    \item[Acknowledgements:] If there is someone who deserves a `thank you', you may add acknowledgements here. If so, make it an unnumbered chapter, i.e., \texttt{\textbackslash chapter*\{Acknowledgements\}}.
    \item[Table of contents:] A table of contents should always be present in a document at the size of a thesis. It is generated automatically using the \texttt{\textbackslash tableofcontents} command. The one generated by this document class also contains the front matter and unnumbered chapters.
    \item[List of figures:] If the thesis contains many figures that the reader might want to refer back to, a list of figures can be included here. It is generated using \texttt{\textbackslash listoffigures}.
    \item[List of tables:] If the thesis contains many tables that the reader might want to refer back to, a list of tables can be included here. It is generated using \texttt{\textbackslash listoftables}.
    \item[List of code listings:] If the thesis contains many code listings that the reader might want to refer back to, a list of code listings can be included here. It is generated using \texttt{\textbackslash lstlistoflistings}.
    \item[Other lists:] If there are other list you would like to include, this would be a good place. Examples could be lists of definitions, theorems, nomenclature, abbreviations, glossary etc. There are no standards for this, but many lists can be generated using the \texttt{description} environment (like, e.g., this list of possible front matter content) within a separate \texttt{\textbackslash chapter*\{\}}.
    \item[Preface or Foreword:] A preface or foreword is a good place to make other personal statements that do not fit whithin the body matter. This could be information about the circumstances of the thesis, your motivation for choosing it, or possibly information about an employer or an external company for which it has been written. Again, use, e.g., \texttt{\textbackslash chapter*\{Preface\}}.
\end{description}

\section{Body Matter}

The body matter consists of the main chapters of the thesis. It starts the Arabic page numbering with page~1. There is a great diversity in the structure chosen for different thesis types. Common to almost all is that the first chapter is an introduction, and that the last one is a conclusion followed by the bibliography.

\subsection{Development Project}
\label{sec:development}

For many bachelor and some master projects in computer science, the main task is to develop something, typically a software prototype, for an `employer' (e.g., an external company or a research group). A thesis describing such a project is typically structured as a software development report whith more or less the following chapters:

\begin{description}
    \item[Introduction:] The introduction of the thesis should take the reader all the way from the big picture and context of the project to the concrete task that has been solved in the thesis. A nice skeleton for a good introduction was given by \textcite{claerbout1991scrutiny}: \emph{review–claim–agenda}. In the review part, the background of the project is covered. This leads up to your claim, which is typically that some entity (software, device) or knowledge (research questions) is missing and sorely needed. The agenda part briefly summarises how your thesis contributes.
    \item[Requirements:] The requirements chapter should lead up to a concrete description of both the functional and non-functional requirements for whatever is to be developed at both a high level (use cases) and lower levels (low level use cases, requirements). If a classical waterfall development process is followed, this chapter is the product of the requirement phase. If a more agile model like, e.g., SCRUM is followed, the requirements will appear through the project as, e.g., the user stories developed in the sprint planning meetings.
    \item[Technical design:] The technical design chapter describes the big picture of the chosen solution. For a software development project, this would typically contain the system arcitechture (client-server, cloud, databases, networking, services etc.); both how it was solved, and, more importantly, why this architecture was chosen.
    \item[Development Process:] In this chapter, you should describe the process that was followed. It should cover the process model, why it was chosen, and how it was implemented, including tools for project management, documentation etc. Depending on how you write the other chapters, there may be good reasons to place this chapters somewhere else in the thesis.
    \item[Implementation:] Here you should describe the more technical details of the solution. Which tools were used (programming languages, libraries, IDEs, APIs, frameworks, etc.). It is a good idea to give some code examples. If class diagrams, database models etc. were not presented in the technical design chapter, they can be included here.
    \item[Deployment:] This chapter should describe how your solution can be deployed on the employer's system. It should include technical details on how to set it up, as well as discussions on choices made concerning scalability, maintenance, etc.
    \item[Testing and user feedback:] This chapter should describe how the system was tested during and after development. This would cover everything from unit testing to user testing; black-box vs. white-box; how it was done, what was learned from the testing, and what impact it had on the product and process.
    \item[Discussion:] Here you should discuss all aspect of your thesis and project. How did the process work? Which choices did you make, and what did you learn from it? What were the pros and cons? What would you have done differently if you were to undertake the same project over again, both in terms of process and product? What are the societal consequences of your work?
    \item[Conclusion:] The conclusion chapter is usually quite short – a paragraph or two – mainly summarising what was achieved in the project. It should answer the \emph{claim} part of the introduction. It should also say something about what comes next (`future work').
    \item[Bibliography:] The bibliography should be a list of quality-assured peer-reviewed published material that you have used throughout the work with your thesis. All items in the bibliography should be referenced in the text. The references should be correctly formatted depending on their type (book, journal article, conference publication, thesis etc.). If \texttt{biblatex} is correctly used as proposed by this template, the formatting will be taken care of automatically. The bibliography should not contain links to arbitrary dynamic web pages where the content is subject to change at any point of time. Such links, if necessary, should rather be included as footnotes throughout the document. The main point of the bibliography is to back up your claims with quality-assured material that future readers will actually be able to retrieve years ahead.
\end{description}

\subsection{Research Project}
\label{sec:resesarch}

For many master and some bachelor projects in computer science, the main task is to gain knew knowledge about something. A thesis describing such a project is typically structed as an extended form of a scientific paper, following the so-called IMRaD (Introduction, Method, Results, and Discussion) model:

\begin{description}
    \item[Introduction:] See \cref{sec:development}.
    \item[Background:] Research projects should always be based on previous research on the same and/or related topics. This should be described as a background to the thesis with adequate bibliographical references. If the material needed is too voluminous to fit nicely in the review part of the introduction, it can be presented in a separate background chapter.
    \item[Method:] The method chapter should describe in detail which activities you undertake to answer the research questions presented in the introduction, and why they were chosen. This includes detailed descriptions of experiments, surveys, computations, data analysis, statistical tests etc.
    \item[Results:] The results chapter should simply present the results of applying the methods presented in the method chapter without further ado. This chapter will typically contain many graphs, tables, etc. Sometimes it is natural to discuss the results as they are presented, combining them into a `Results and Discussion' chapter, but more often they are kept separate.
    \item[Discussion:] See \cref{sec:development}.
    \item[Conclusion:] See \cref{sec:development}.
    \item[Bibliography:] See \cref{sec:development}.
\end{description}

\subsection{Monograph PhD Thesis}
\label{sec:monograph}

Traditionally, it has been common to structure a PhD thesis as a single book – a \emph{monograph}. If the thesis is in the form of one single coherent research project, it can be structured along the lines of \cref{sec:resesarch}. However, for such a big work that a PhD thesis constitutes, the tasks undertaken are often more diverse, and thus more naturally split into several smaller research projects as follows:

\begin{description}
    \item[Introduction:] The introduction would serve the same purpose as for a smaller research project described in \cref{sec:development}, but would normally be somewhat more extensive. The \emph{agenda} part should inform the reader about the structure of the rest of the document, since this may vary significantly between theses.
    \item[Background:] Where as background chapters are not necessarily needed in smaller works, they are almost always need in PhD thesis. They may even be split into several chapters if there are significantly different topics to cover. See \cref{sec:resesarch}.
    \item[Main chapters:] Each main chapter can be structured more or less like a scientific paper. Depending on how much is contained in the introduction and background sections, the individual introduction and background sections can be significantly reduced or even omitted completely.
    \begin{itemize}
        \item (Introduction)
        \item (Background)
        \item Method
        \item Results
        \item Discussion
        \item Conclusion
    \end{itemize}
    \item[Discussion:] In addition to the discussions within each of the individual chapters, the contribution of the thesis \emph{as a whole} should be thoroughly discussed here.
    \item[Conclusion:] In addition to the conclusions of each of the individual chapters, the overall conclusion of the thesis, and how the different parts contribute to it, should be presented here. The conclusion should answer to the research questions set out in the main introduction. See also \cref{sec:development}.
    \item[Bibliography:] See \cref{sec:development}.
\end{description}

\subsection{Compiled PhD Thesis}
\label{sec:compiledphd}

Instead of writing up the PhD thesis as a monograph, compiled PhD theses (also known as stapler theses, sandwich theses, integrated theses, PhD by published work) consisting of reproductions of already published research papers are becoming increasingly common. At least some of the papers should already have been accepted for publication at the time of submission of the thesis, and thus have been through a real quality control by peer review.

\begin{description}
    \item[Introduction:] See \cref{sec:monograph}.
    \item[Background:] See \cref{sec:monograph}.
    \item[Main contributions:] This chapter should sum up \emph{and integrate} the contribution of the thesis as a whole. It should not merely be a listing of the abstracts of the individual papers – they are already available in the attached papers, and, as such, not needed here.
    \item[Discussion:] See \cref{sec:monograph}.
    \item[Conclusion:] See \cref{sec:monograph}.
    \item[Bibliography:] See \cref{sec:development}.
    \item[Paper I:] First included paper with main contributions. It can be included verbatim as a PDF. The publishers PDF should be used if the copyright permits it. This should be checked with the SHERPA/RoMEO database\footnote{\url{http://sherpa.ac.uk/romeo/index.php}} or with the publisher. Even when it is no general permission by the publisher, you may write and ask for one.
    \item[Paper II:] etc.
\end{description}

\section{Back Matter}

Material that does not fit elsewhere, but that you would still like to share with the readers, can be put in appendices. See \cref{app:additional}.
\end{comment}